Preprocessing: filtering (experiment)

### 2021-12-01 analysis/filtering.Rmd
upload filtering
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Onset
## Detect erroneous trials
```{r, echo = FALSE}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

## Detect erroneous trials
```{r, echo = FALSE}
dt_error_offset <- checker(dt_offset, dt_ideal)

>>>>

# Onset
## Detect erroneous trials
```{r onset, echo = FALSE}
dt_error_onset <- checker(dt_onset, dt_ideal)

@@

## Detect erroneous trials
```{r offset, echo = FALSE}
dt_error_offset <- checker(dt_offset, dt_ideal)
